The Globular Cluster System of the Auriga Simulations

### 2019-04-25 AurigaGCS.tex
Wrote four paragraphs for the introduction (deliberately w/o references)

\section{Introduction}
Globular clusters (GC)s are omnipresent, bright, old, and amongst the simplest
stellar configurations in the Universe. Their visbility and ubiquity make it
possible to obtain integrated GC quantities within the Virgo Supercluster.
Moreover, GCs inherit characteristics from their natal gas and GC systems show
correlations with properties of (the field stars in) their host galaxies.
% For
% example, the mean metallicity of GC systems in early-type galaxies correlates with
% the galactic metallicity (van den Bergh 1975, Brodie \& Huchra 1991) as well as
% with the luminosity, and possibly the mass (Larsen 2001; Peng 2006).
The old ages
are consistent with formation before, during, or shortly after the initial
collapse of the proto-galaxy and GCs have been present within galaxies for nearly
a Hubble time. In theory, all of these characteristics make GC systems excellent
tracers of the formation and evolution of their parent galaxies, if the formation
of GCs themselves is well-understood.

Most galaxies host GC systems with a bimodal colour distribution, indicative of
a bimodal metallicity distribution. The Milky Way (MW) GC system (GCS) can be
split up in a metal-rich (red) and metal-poor (blue) subpopulation divided at
[Fe/H]~$=-1$ \citep[e.g.][]{Harris2001}, although slightly different values can
also be found in the literature. The two subpopulations are believed to be
associated to the galactic disk, respectively the stellar halo
\citep[e.g.][]{1985ApJ...293..424Z}. The latter is supported by observed similarities
between the spatial distribution and chemical signature of the `blue' GCs show
and stars in the stellar halo \citep{2008A&ARv..15..145H}. Moreover, relative
age-estimates indicate that the metal-poor subpopulation may be $1.5$~Gyr younger
than the metal-rich counterpart \citep{2005AJ....130..116D}.

Several formation scenarios could explain the observed bimodality, see
\citet{2006ARA&A..44..193B} for a review of extragalactic GCs and galaxy
formation. The authors argue that the observed metal-rich and metal-poor

>>>>

\section{Introduction}
Globular clusters (GC)s are omnipresent, bright, old, and amongst the simplest
stellar configurations in the Universe. The globular cluster systems (GCS) of
the Milky Way (MW) and the Andromeda galaxy (M31) have been studied extensively 
over the last decades. More recent analyses of the Gaia data shed new light on the 
chemical- and structural properties, and on the phase-space distribution 
of the MW GC system.
% https://arxiv.org/abs/1805.01408
% https://arxiv.org/abs/1807.09775
% https://www.aanda.org/articles/aa/abs/2018/08/aa32698-18/aa32698-18.html
Moreover, the visbility and ubiquity of GCs makes it possible to obtain integrated 
properties of GCs within the Local Group with reasonable certainty, and even of 
those that are located further away within the Virgo Supercluster.

The natal gas regions in which globular clusters form inherit key characteristics 
from their parent (proto-)galaxies. GC populations, in turn, will therefore retain 
a record of these properties and offer a unique insight into the detailed chemical 
and dynamical evolution history of their host galaxies. In theory, this information 
should be readily available and easily observable in the low redshift Universe, given 
that GCs survive nearly a Hubble time of evolution within the violent galactic 
environments they live in. However, a prerequisite to infer galactic histories
from observations of GC systems is to understand the subtleties of the GC formation
and evolution itself.

Several formation scenerarios are consistent with the observations of globular 
cluster populations. One important constraint comes from bimodality in the 
colour distribution, which is indicative of a bimodality in the underlying 
metallicity distribution of GC systems. For example, GCs in the MW are typically
split up in a metal-rich (red) and metal-poor (blue) subpopulation divided at
[Fe/H]~$=-1$ \citep[e.g.][]{Harris2001}, although slightly different values can
also be found in the literature. The two subpopulations are believed to be
associated to the galactic disk, respectively the stellar halo
\citep[e.g.][]{1985ApJ...293..424Z}. The latter is supported by observed similarities
between the spatial distribution and chemical signature of the `blue' GCs show
and stars in the stellar halo \citep{2008A&ARv..15..145H}. Moreover, relative
age-estimates indicate that the metal-poor subpopulation may be $1.5$~Gyr younger
than the metal-rich counterpart \citep{2005AJ....130..116D}.

\citet{2006ARA&A..44..193B} for a review of extragalactic GCs and galaxy
formation. The authors argue that the observed metal-rich and metal-poor

In a recent study Chiou et al. speculate that GCs may form in supersonically
induced gasseous objects at high redshifts. These objects are free of dark matter 
and populate a mass range consistent with the typical mass scale of GCs. 
Interestingly, the authors find present-day absolute visual magnitude and 
characteristic scales consistent with GCs in the Local group, based on a 
rudimentary star formation model.
